\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2021-02-09 icra-2021.tex
added the proof the the theorem

\begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (a period of the plan is valid, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic). Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
\end{thm}
\begin{proof}
  The proof is based on mathematical induction. 
  Base case: *

  Induction step: *

\end{proof}

>>>>

\begin{thm}[Valid periodic plan]\label{thm:state-vs-energy}  
  Suppose Assumption~\ref{assm:valid}, Lemma~\ref{lem:eqv}, and Proposition~\ref{assm:periodic} hold (a period of the plan is valid, its energy evolution is described by Equation~(\ref{eq:state-perf}), and the plan is periodic). Then the plan is valid and its energy evolution modeled by the periodic energy model in Section~\ref{sec:model}.
\end{thm}
\begin{proof}
  From Definition~\ref{def:valid} we know that there exists a $\mathcal{J}\subseteq[l]^+$ where the path is valid, and from Proposition~\ref{prop:rank} we know that the path is periodic. Hence if the set $\mathcal{J}$ is valid, then also the set $i[j-n+1,j]\subseteq[l]^+$ is valid for a given $i$. From Assumption~\ref{assm:valid} we note that $i\in[l/n]^+$ and thus under the assumptions $\mathcal{J}=[l]^+$. Due to the periodicity, Lemma~\ref{lem:eqv} tells us that we can use the proposed approach to model the energy.
\end{proof}

We can thus output a valid control sequence for the initial plan $\Gamma$. For practical means, we consider some realistic constraints to the energy of a flying UAV. We illustrate such constraints in the following subsection.
